\sys: Light-touch Data-Parallel Shell Processing

### 2020-09-25 paper/draft.tex
Update paper

%% EuroSys 2021 -- 12 pages limit
\documentclass[sigplan,review,anonymous]{acmart}
\acmSubmissionID{TBD}
\renewcommand\footnotetextcopyrightpermission[1]{}

@@

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
% Limit: 25 pages
% https://icfp20.sigplan.org/track/icfp-2020-papers#Call-for-Papers
%% \documentclass[acmsmall,10pt,review,anonymous]{acmart}
%% \settopmatter{printfolios=false,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[sigplan]{acmart}\settopmatter{}

% \acmSubmissionID{248}

@@

@@

\subsection*{Acknowledgements}
% Dumping people so that we don't forget
We want to thank 
  Andr\'e DeHon,
  Ben Karel,
  Jean-S\'ebastien L\'egar\'e, and 
  Nick Roessler.
This material is based upon work supported by DARPA contract no. HR00112020013 (ALRSCC) and NSF award CCF 1763514.
%% \grantsponsor{GS100000001}{National Science
%%   Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
%% No.~\grantnum{GS100000001}{nnnnnnn} and Grant
%% No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
%% conclusions or recommendations expressed in this material are those
%% of the author and do not necessarily reflect the views of the
%% National Science Foundation.

>>>>

%% EuroSys 2021 -- 12 pages limit
\documentclass[sigplan, review, screen, anonymous]{acmart}
\acmSubmissionID{49}
\renewcommand\footnotetextcopyrightpermission[1]{}
\settopmatter{printfolios=false,printccs=false,printacmref=false}

@@

@@

\todo{Concurrent to our work, POSH is a framework that accelerates shell applications with I/O-heavy components. XXX}

@@

% \subsection*{Acknowledgements}
% % Dumping people so that we don't forget
% We want to thank 
%   Andr\'e DeHon,
%   Ben Karel,
%   Jean-S\'ebastien L\'egar\'e, and 
%   Nick Roessler.
% This material is based upon work supported by DARPA contract no. HR00112020013 (ALRSCC) and NSF award CCF 1763514.

%% \grantsponsor{GS100000001}{National Science
%%   Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
%% No.~\grantnum{GS100000001}{nnnnnnn} and Grant
%% No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
%% conclusions or recommendations expressed in this material are those
%% of the author and do not necessarily reflect the views of the
%% National Science Foundation.
